Study locations

### 2023-10-15 Scripts/1_Visualisation/Map_study_locations.Rmd
preparing taxonomic info of polls

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red", "gray")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)

>>>>

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red", "gray","violetred",
"coral4", "plum1")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)
